### 2023-06-08 resources/tools/tools.tex

\begin{tabularx}{\textwidth}{c|c|l}
  \hline \textbf{Język programowania} & \textbf{Biblioteki}      & \textbf{Nazwa podprojektu} \\ \hline
   Python                             & NumPy                    & cssfinder\_backend\_numpy \\
   Python                             & NumPy, Cython            & cssfinder\_backend\_numpy \\
   Python                             & NumPy, Numba             & cssfinder\_backend\_numpy \\
   Rust                               & Ndarray                  & cssfinder\_backend\_rust \\
   Rust                               & Ndarray, OpenBLAS        & cssfinder\_backend\_rust \\ \hline
\end{tabularx}