### 2023-09-16 resources/tools/tools.tex

\begin{tabularx}{\textwidth}{l|l|l}
  \hline \textbf{Język programowania} & \hspace{1.5cm} \textbf{Biblioteki}                    & \hspace{1cm} \textbf{Nazwa podprojektu}              \\ \hline
  \hspace{0.5cm} Python               & \hspace{0.5cm} NumPy                   \hspace{0.5cm} & \hspace{0.7cm} cssfinder\_backend\_numpy  \\
  \hspace{0.5cm} Python               & \hspace{0.5cm} NumPy, Cython           \hspace{0.5cm} & \hspace{0.7cm} cssfinder\_backend\_numpy  \\
  \hspace{0.5cm} Python               & \hspace{0.5cm} NumPy, Numba            \hspace{0.5cm} & \hspace{0.7cm} cssfinder\_backend\_numpy  \\
  \hspace{0.5cm} Rust                 & \hspace{0.5cm} Ndarray                 \hspace{0.5cm} & \hspace{0.7cm} cssfinder\_backend\_rust   \\
  \hspace{0.5cm} Rust                 & \hspace{0.5cm} Ndarray, OpenBLAS       \hspace{0.5cm} & \hspace{0.7cm} cssfinder\_backend\_rust   \\ \hline
\end{tabularx}